### 2012-05-10 Rctl/inst/doc/manual.Rnw
[Rctl] More manual updates

\textbf{\sffamily Abstract}: Correlated Trait Loci (CTL) mapping using the R package 'ctl'
\vfill
\noindent \verb|Software:      http://www.mapctl.org/download.html|\\
\noindent \verb|Manual:        http://www.mapctl.org/manual.html|\\
\noindent \verb|Source-code:   http://www.github.com/DannyArends/ctl|\\
\noindent \verb|E-mail:        Danny.Arends@Gmail.com|
\newpage

@@

\emph{CTLscan options}\\
The genotype matrix and the $geno.enc$ parameter, the phenotype matrix, the important $n.perms$ 
parameter, which should be set to as many as possible, especially when publishing any results, 
but for a quick scan 100 is ussualy sufficient:
<<echo=TRUE,eval=FALSE>>=
ctls_quick_scan      <- CTLscan(geno,traits,n.perm=100)
ctls_for_publication <- CTLscan(geno,traits,n.perm=15000)
@

@@

<<echo=TRUE,eval=FALSE>>=
cofactors <- mqmautocofactors(multitrait, 30)
mqm_qtls  <- mqmscanone(multitrait, cofactors=cofactors, pheno.col=1:24)[,-c(1,2)]
ctls_mqm  <- CTLscan.cross(multitrait, pheno.col=1:2, have.qtl=qtls)
@

CTLs can be condition dependant just like QTL, so if one has multiple conditions or treatments. we 
need to acomodate that in the underlying models. If no QTLs are supplied the internal QTL mapping 
routine is used, which can deal with just a single condition per individual. An environmental 
condition can be specified by the $conditions$ parameter:

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:81 were in condition A / e.g. treatment
#Specify that individuals 82:162 were in condition B / e.g. control
conditions <- c(rep(1,81),rep(2,81))
ctls <- CTLscan(geno, traits, conditions=conditions)
@

>>>>

\textbf{\sffamily Abstract}: Tutorial for the Correlated Trait Loci (CTL) mapping to reconstruct
genetic regulatory networks using the R package 'ctl' and the mapctl commandline tool. This 
tutorial is targetted at people with a basic understanding of genetics and would like to analyse
there inbred cross or natural population. Main focus will be explaining the functionality of the 
software, and a how-to on loading datasets via Excel, tab delimited files (.csv) and R/qtl. In 
the methodology and background only a short introduction in CTL mapping theory is given.

\vfill
\noindent \verb|Software:      http://www.mapctl.org/download.html|\\
\noindent \verb|Manual:        http://www.mapctl.org/manual.html|\\
\noindent \verb|Source-code:   http://www.github.com/DannyArends/ctl|\\
\noindent \verb|E-mail:        Danny.Arends@Gmail.com|
\newpage

@@

\emph{CTLscan options}\\
The genotype matrix and the $geno.enc$ parameter, if data is of a different encoding then the 
standard 1 / 2 it can be specified by using the $geno.enc$ parameter.

<<echo=TRUE,eval=FALSE>>=
#Load a dataset with "AA" and "AB" genotypes
ctls <- CTLscan(geno,traits,geno.enc=c("AA","AB"))
@

The important $n.perms$ parameter, which should be set to as many as possible, especially 
when publishing any results, but for a quick the default of 100 is sufficient:
<<echo=TRUE,eval=FALSE>>=
ctls_quick_scan      <- CTLscan(geno,traits,n.perm=100)
ctls_for_publication <- CTLscan(geno,traits,n.perm=15000)
@

CTLs could be condition dependant just like QTL, so if one has multiple conditions or 
treatments. we need to accomodate that in the underlying models. 
{\color{red} \emph{\bf{ \\\\NOTE: Current version doesn't handle conditions (only the QTL are compensated). \\\\}}} 
If no QTLs are supplied the internal QTL mapping routine is used, which can deal with just a single condition per 
individual. An environmental condition can be specified by the $conditions$ parameter:

<<echo=TRUE,eval=FALSE>>=
#Specify that individuals 1:51 were in condition A / e.g. treatment A
#Specify that individuals 52:100 were in condition B / e.g. treatment B 
#Specify that individuals 101:162 were in condition C / e.g. control
conditions <- c(rep(1,51),rep(2,49),rep(2,62))
ctls <- CTLscan(geno, traits, conditions=conditions)
@

@@

<<echo=TRUE,eval=FALSE>>=
cofactors <- mqmautocofactors(multitrait, 30)
mqm_qtls  <- mqmscan(multitrait, cofactors=cofactors, pheno.col=1:24)[,-c(1,2)]
ctls_mqm  <- CTLscan.cross(multitrait, pheno.col=1:2, have.qtl=qtls)
@
